Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-14 presentations/bsa_2020-07-27/index.Rmd
Move some presentation-only functions to presentation rmd

trend_line_theme <- function () {
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_line(size = 0.1, color = "dark grey"),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank()
  )
}
```

@@

source(here::here("R/functions.R"))

# Load targets
loadd(list = c(
  "ses_div_ferns_spatial",
  "occ_point_data_ferns",
  "protected_areas"),
  cache = ja_fern_cache)

>>>>

trend_line_theme <- function () {
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_line(size = 0.1, color = "dark grey"),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank()
  )
}

map_theme_pp <- function() {
  theme(
    panel.grid.major = element_line(color = "white", size = 0.1),
    panel.background = element_rect(fill = "grey70"),
    axis.ticks = element_blank()
  )
}

map_theme_pp_light <- function() {
  theme(
    panel.grid.major = element_line(color = "white", size = 0.1),
    panel.background = element_rect(fill = "grey90"),
    axis.ticks = element_blank()
  )
}

source(here::here("R/functions.R"))
```

@@

# Load targets
loadd(list = c(
  "traits_for_dist",
  "ses_div_ferns_spatial",
  "occ_point_data_ferns",
  "protected_areas"),
  cache = ja_fern_cache)
